---
name: James (Jay) Brophy
position: "Professor of Medicine"
address: "McGill University"
phone: 514 934-1934
profilepic: brophy.jpg
www: www.brophyj.com
email: "james.brophy@mcgill.ca"
twitter: brophyj
github: brophyj
linkedin: brophyj
# orcid: ff837659-6cab-4980-bc45-51d836e4fd6b
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Slightly contrarian cardiologist living and working in Montreal Canada"
output: vitae::hyndman
linkcolor: red
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# ref https://github.com/ropenscilabs/vitae
library(tidyverse)
library(RefManageR)
library(vitae) # devtools::install_github("ropenscilabs/vitae")
library(knitr)

```

# Education
```{r education}
library(rorcid)
library(vitae)
x <- orcid_auth()

# seems to get right info
# x
#[1] "Bearer ff837659-6cab-4980-bc45-51d836e4fd6b"

Sys.setenv(ORCID_TOKEN = "ff837659-6cab-4980-bc45-51d836e4fd6b") #may need to run this line separate first before knitting

edu <- rorcid::orcid_educations("0000-0001-8049-6875")

edu <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0001-8049-6875")$`0000-0001-8049-6875`$`affiliation-group`$summaries
)
edu %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )

```

# Current Research Funding (PI) 

```{r awards}
library(tibble)
library(vitae)
tibble::tribble(
  ~name, ~event, ~location, 
  "Appui à la recherche en évaluation des technologies et des pratiques de pointe dans les CHU (Health Technology and Evidence Based Medicine)", "Fonds de Recherche Quebec Sante (FRQS)", "July 2018-23",
 "Ticagrelor compared to clopidogrel in acute coronary syndromes - the TC4 comparative effectiveness study", "Canadian Institutes of Health Research (CIHR) Project Grant Total Funding - $309,825","2018/4 - 2021/3") %>% 
  detailed_entries(
    what = name,   #when = year,
    with = event,
    where = location
  )
```

# Awards 
```{r}
library(tibble)
library(vitae)
tibble::tribble(
  ~name, ~event, ~location, 
  "Fellow Canadian Academy of Health Sciences", "", "Sept 2018",
  "Fellow Canadian Cardiovascular Society", "", "May 2017") %>%
  detailed_entries(
    what = name,   #when = year,
    with = event,
    where = location
  )
```

# Publications 

All publications (`r nrow(brophy <- scholar::get_publications("IXoZb4wAAAAJ") %>% 
    filter( !grepl('Response|reply|Renewed|Reply', title)))` on `r Sys.Date()`) as recorded in Google Scholar can be found [**here**](https://scholar.google.com/citations?user=IXoZb4wAAAAJ&hl=en)        
Citations 15,215, h-index 53

       
```{r fig.height=3}
#plot over time from 2004-
library(ggplot2)
brophy <- scholar::get_publications("IXoZb4wAAAAJ") %>% 
    filter( !grepl('Response|reply|Renewed|Reply', title))

trend <- brophy %>%
  filter(year >2007) %>%
  group_by(year) %>%
  summarise(n=n())
ggplot(trend,aes(year,n)) +
  geom_point() +
  geom_line() +
  # ggtitle("Publications according to Google Scholar") +
    labs(subtitle=" Includes letters, editorials as well as original articles") +
    ylab("Number of Publications") +
    xlab("Year") +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 8)) +
    theme_bw()

```
        
        
        
# Publications 2020        
 
```{r}
brophy <- scholar::get_publications("IXoZb4wAAAAJ") %>% 
    filter(year == 2020   & !grepl('Response|reply|Renewed|Reply', title)) %>%
    arrange(desc(year))

top <- brophy[, c("title", "journal", "year", "author", "cites")]
top$title <- as.character(top$title)
top %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal)
   

# top_n(brophy, 16) %>%
#    detailed_entries(
#    what = title,
#    when = year,
#    with = author,
#    where = journal) 


# top_n(XX)  filter XX publications as needed for formating purposes in pdf
``` 


# Publications 2019   

```{r}
brophy <- scholar::get_publications("IXoZb4wAAAAJ") %>% 
    filter(year == 2019   & !grepl('Response|reply|Renewed|Reply', title)) %>%
    arrange(desc(year))

top <- brophy[, c("title", "journal", "year", "author", "cites")]
top$title <- as.character(top$title)
top %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal)
   

# top_n(brophy, 16) %>%
#    detailed_entries(
#    what = title,
#    when = year,
#    with = author,
#    where = journal) 


# top_n(XX)  filter XX publications as needed for formating purposes in pdf
```



```{r echo=FALSE, eval=FALSE}
# Publications 2018   
brophy <- scholar::get_publications("IXoZb4wAAAAJ") %>% 
    filter(year == 2018  & !grepl('Response|reply|Renewed|Reply', title)) %>%
    arrange(desc(year))

top <- brophy[, c("title", "journal", "year", "author", "cites")]
top$title <- as.character(top$title)
top %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal)
```



# Top citations

```{r top}
brophy <- scholar::get_publications("IXoZb4wAAAAJ") %>%
    arrange(desc(cites))

top <- brophy[3:7, c("title", "journal", "year", "author", "cites")]
top$title <- as.character(top$title)
top$title[2] <- c("Beta Blockers in congestive heart failure: a Bayesian meta-analysis")
top %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal,
    why = glue::glue("cites: {cites}"))
```
# Talks (2019)

```{r talks19}
library(tibble)
library(vitae)
tibble::tribble(
  ~name, ~event, ~location, 
  "Evaluating evidence from meta-analyses of randomized controlled trials using a Bayesian approach", "McGill University Health Center Health Technology Symposium", "Montreal QC July 2019",
  "Practical session: R for health economic analyses", "McGill University Health Center Health Technology Symposium", "Montreal QC July 2019",
   "Critical review of the medical literature", "McGill University Epidemiology (600) guest lecture", "Montreal QC July 2019",
"Critical analysis of the health technology assessment", "McGill University Epidemiology (600) guest lecture", "Montreal QC July 2019",
"Dual antiplatelet therapy 2019 - An Integrated Approach", "Jewish General Hospital", "Montreal QC Oct 4 2019",
  "Dual antiplatelet therapy 2019 - Beyond guidelines", "McGill University Health Center Cardiology Grand Rounds", "Montreal QC Sept 26 2019",
  "Dual antiplatelet therapy - The totality of the evidence and its uncertainty", "McGill University Health Center Medicine Grand Rounds", "Montreal QC Sept 24 2019",
  "Dual antiplatelet therapy - An MUHC initiated comparative effectiveness study", "McGill University Health Center Cardiology Grand Rounds", "Montreal QC Sept 20 2018") %>% 
  detailed_entries(
    what = name,   #when = year,
    with = event,
    where = location
  )
```

# Talks (2018)

```{r talks18}
library(tibble)
library(vitae)
tibble::tribble(
  ~name, ~event, ~location, 
  "Revascularization 2018 - (Personal reflections on personalized medicine)", "McGill University Health Center Cardiovascular Multidisciplinary Rounds", "Montreal QC Sept 20 2018",
  "Evidence to inform practice: Promising avenues and dead ends (Panel)", "European Society of Cardiology","Munich Germany Aug 30 2018",
  "Observational study designs: successes, limitations, pitfalls, lessons learned", "McGill University Epi 600 guest lecture", "Montreal June 5 2018",
  "Health technology assessment and economic analyses", "McGill University Epi 600 guest lecture", "Montreal June 19 2018",
  "Observational studies in cardiology – case of NSAID cardio toxicity", "McGill Epidemiology Winter Seminar Series", "Montreal February 26 2018", 
  "The crisis in medical guidelines", "Guest lecture The Crisis in Health Research seminar course", "Montreal Feb 2018") %>% 
  detailed_entries(
    what = name,   #when = year,
    with = event,
    where = location
  )
```

```
```{r publications}
temp <- bibliography_entries("My_endnote.bib")
temp$author <- gsub("[ and]",", ", temp$author)
```



